% Based on the template from Pandoc 2.13. Custom sections are marked
% 'CUSTOM'. Customisations go in included files where possible, but
% this isn't always possible.
% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames*,x11names*}{xcolor}
%
\documentclass[
  12pt,
  british,
  a4paper,
]{article}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
  \setmainfont[]{Times New Roman}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage{fancyvrb}
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The Title Is Baz},
  pdfauthor={The Author},
  pdflang={en-GB},
  pdfsubject={Version: 3662361-dirty, Sun Apr 11 16:01:37 2021 +0200},
  colorlinks=true,
  linkcolor={black},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\VerbatimFootnotes % allow verbatim text in footnotes
\usepackage[a4paper]{geometry}
\usepackage[normalem]{ulem}
% Avoid problems with \sout in headers with hyperref
\pdfstringdefDisableCommands{\renewcommand{\sout}{}}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\usepackage{bold-extra}
\usepackage[perpage,symbol*]{footmisc}

% This makes horizontal rules for section breaks appear as three stars, rather
% than a solid line. Unfortunately 'rule' is used in other places, such as
% footnotes - hence the conditional gymnastics. Hopefully it doesn't break
% anything else.
\newif\iffootnote
\let\Footnote\footnote
\renewcommand\footnote[1]{\begingroup\footnotetrue\Footnote{#1}\endgroup}

\let\OldRule\rule
\renewcommand{\rule}[2]{\iffootnote\OldRule{#1}{#2}\else* * *\fi}
\usepackage{titletoc}
\titlecontents{section}[2.4em]{}{}{\hspace*{-2.4em}}{ \titlerule\contentspage}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[variant=british]{english}
\else
  \usepackage[main=british]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{The Title Is Baz}
\author{The Author}
\date{23 February 2019}

\begin{document}
\maketitle

\frenchspacing

{
\hypersetup{linkcolor=}
\setcounter{tocdepth}{1}
\tableofcontents
}

% CUSTOM
% END CUSTOM

\hypertarget{this-is-a-section}{%
\section{This is a section}\label{this-is-a-section}}

This is some test text. This is formatted in \emph{italics} and
\textbf{bold}, with - various -- dashes---, and trailing dots\ldots{}

`These quotes should be curly,' and ``so should these.'' There should be
a blank line before the next paragraph:

~

And then we do a simple include:

Text before a section in simple include.

\hypertarget{section-in-simple-include}{%
\section{Section in simple include}\label{section-in-simple-include}}

\begin{quote}
This is a quote block. It should be indented slightly and shouldn't
contain a line break.
\end{quote}

\begin{quote}
This is a quoted line block. It should be indented slightly\\
and have a \emph{line break} after `slightly', and \textbf{formatting}.
\end{quote}

Text before recursive include, with \emph{italic}, \textbf{bold},
``curly quotes,'' and--- an em dash.

Text before section in recursive include.

\hypertarget{section-in-recursive-include}{%
\section{Section in recursive
include}\label{section-in-recursive-include}}

Text in recursive include, with \emph{italic}, \textbf{bold}, ``curly
quotes,'' and--- an em dash.

\hypertarget{subsection-in-recursive-include}{%
\subsection{Subsection in recursive
include}\label{subsection-in-recursive-include}}

\begin{quote}
``These literal double curly quotes, used where smart\\
quotes gets it wrong, curl the right way even though\\
they're on different lines.''
\end{quote}

\begin{quote}
`These literal single curly quotes, used where smart\\
quotes gets it wrong, curl the right way even though\\
they're on different lines.'
\end{quote}

Test text test text test text. After this line there should be stars.

\begin{center}\rule{0.5\linewidth}{0.5pt}\end{center}

And then there should be some text \textsuperscript{in~superscript} and
\textsubscript{in~subscript}, and a footnote\footnote{This is a
  footnote. It should appear at the bottom of the page.} with a star, a
footnote\footnote{Another footnote.} with a dagger, and this should be
\texttt{monospace}.

Text after recursive include. Here is a pound sign (£), a euro sign (€),
and three letters with accents: ëóû.

\hypertarget{second-section-in-simple-include}{%
\section{Second section in simple
include}\label{second-section-in-simple-include}}

Test text.

Text after simple include.

\hypertarget{subsection}{%
\subsection{Subsection}\label{subsection}}

This is a new paragraph. This text is \textsc{Small Caps}.

\hypertarget{this-is-a-second-section}{%
\section{This is a second section}\label{this-is-a-second-section}}

And this is \emph{even more italic text}.

\end{document}
